\documentclass[]{article}

\title{Corrections to Page Proofs for ``Knowledge, Bets and Interests''}
\author{Brian Weatherson}

\usepackage{fullpage}

\begin{document}

\maketitle

All of the tables have gridlines around every cell. I would prefer that all these gridlines were deleted, but if it is a house style to include them, then I have no objection to leaving them in.

On page 87, there are a couple of things which could be neater. Line 12 starts with $x \in [0,1]$. But for some reason the $\in$ has been italicised, and there isn't much space between the characters. So that could look better. Later in that line, the expression $\Pr(p|p) = 1$ has been split over two lines, and it would be better to have it on a single line.

Later that page, 11 lines from the bottom, there is a large gap between \textit{What is the probability of p to one decimal place?} and the following period, which perhaps could be reduced.

From page 91 onwards, what should be occurrences of $\varphi$ are consistently replaced with $\Pi$. I'm not sure how or why this happened, but it looks bad, especially because the $\Pi$'s are so large, and it would be better to have $\varphi$ back.

In the table on page 93, the 2nd and 3rd columns are of unequal width. They should be the same width.  The same thing happened with the table on the top of Page 95.  And they should not be a period in the bottom right cell of that table.

One of the symbols in the header row of the table on page 94 is mistaken. It should be $\wedge$ not $3$. So the headers should read: $p \wedge q$, $p \wedge \neg q$, $\neg p$.  And columns should be equal width. Or at least the last 3 columns should be equal width.

On page 96, 2 paragraphs after the quote, there is a missing word. The sentence ``Assume Lewis corrects the incoherence in his beliefs, and drops the belief ￼￼￼that Nassau Street the railway are roughly parallel.'' should read ``Assume Lewis corrects the incoherence in his beliefs, and drops the belief ￼￼￼that Nassau Street \textbf{and} the railway are roughly parallel.'' (The bolding should not be included, I've just bolded the `and' to make clear it is what's to be added.)

On page 98, line 16, the word `Objection' should be in italics.  On line 17, the `p'  at the end of the sentence should also be in italics.

In the bibliography, something odd happened with the doi references. See, for example, the very first citation, to Blome-Tillman's paper. At the end there is a link which reads

\begin{quote}
http://dx.doi.org/10.1111/j.1933-1592.2009.00280.xdoi:10.1111/j.1933-1592.2009.00280.x
\end{quote}

What it should say is simply

\begin{quote}
doi:10.1111/j.1933-1592.2009.00280.x
\end{quote}

That is, the url should be eliminated, and the doi be all that remains. There are 12 references that are affected by this.

The Feltz and Zarpentine paper is now in print. (It is listed as forthcoming on the page proofs.) The citation information is: \textit{Philosophical Psychology}, vol 23, number 5, October 2010, 683-706, doi: 10.1080/09515089.2010.514572.


\end{document}